SunPy - Python for Solar Physics

### 2014-01-23 3-5-Database.tex
removed microseconds from output

\begin{listing}
\begin{minted}{python}
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
id observation_time_start wavemin        wavemax           download_time             
-- ---------------------- -------        -------           -------------             
1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525397
2  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525469
3  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35.525532
4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429665
5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429731
6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53.429792
\end{minted}
\caption{Displaying database entries in a table.}
\label{code:db_2}
\end{listing}

>>>>

\begin{listing}
\begin{minted}{python}
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax', 'download_time'])
id observation_time_start wavemin        wavemax           download_time      
-- ---------------------- -------        -------           -------------      
1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
2  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
3  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05 2014-01-18 19:21:35
4  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
5  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
6  2011-09-19 23:33:40    0.413280643067 7.29318781883e-05 2014-01-18 19:24:53
\end{minted}
\caption{Displaying database entries in a table.}
\label{code:db_2}
\end{listing}
